Approximate State Abstraction

### 2016-01-31 paper/paper.tex
Cleaned up phi model proof

% --- SECTION: Introduction ---
\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems. However, the knowledge available to a learning agent at any given moment is approximate \dnote{Change this sentence}. Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction. This work characterizes what is ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.

@@

{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
\begin{equation}
\label{eq:lemma2}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma(|\mcS-1|\epsilon)}{(1-\gamma)^3}
\end{equation}

{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound. Consequently $\epM$ abstractions are interpretable as an instantiation of of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.

@@

\begin{align*}
B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
&\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in \mcS_G}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
&\text{By the similarity of transitions of grouped states under $\epM$:}\\
& \leq \epsilon + \gamma \sum_{s_A \in \mcS_A} \epsilon Q_{max} \\
&\leq \epsilon + \gamma|\mcS|\epsilon Q_{max}\\
&\text{Applying 0-1 reward normalization and algebra:}\\
& \leq \frac{\epsilon + \gamma(|\mcS| - 1) \epsilon}{1-\gamma}
\end{align*}

Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1, this yields Equation \ref{eq:lemma2}.

@@

% NChain Compression Visuals.
\begin{figure}[h]
\subfigure[Ground NChain]{
\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
\subfigure[Abstract NChain]{
\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
\label{fig:nchain-visual}
\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under $\epQ$, with $\epsilon=0.5$}
\end{figure}

@@

% Taxi Compression Visuals
\begin{figure}[h]
\subfigure[Ground Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
\subfigure[Abstract Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
\label{fig:taxi-visual}
\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under $\epQ$, with $\epsilon=0.03$}
\end{figure}

@@

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Minefield MDP and Abstract MDP, under $\epQ$, with $\epsilon=1.1$}
\end{figure}

@@

% Random Compression Visuals
\begin{figure}
\subfigure[Ground Random]{
\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
\subfigure[Abstract Random]{
\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Random MDP and Abstract Random MDP, under $\epQ$, with $\epsilon=0.2$}
\end{figure}

>>>>

% --- SECTION: Introduction ---
\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems. However, the knowledge available to a learning agent at any given moment is approximate \dnote{Change this sentence}. Thus, agents must determine when their knowledge is sufficiently accurate to form the basis of abstraction. This work characterizes what ``sufficiently accurate" information for abstraction amounts to in the context of planning and \ac{RL} in \acp{MDP}.

@@

{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
\begin{equation}
\label{eq:lemma2}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{2\epsilon + 2\gamma((|\mcS_G|-1)\epsilon)}{(1-\gamma)^3}
\end{equation}

{\bf Proof:} Our proof proceeds as follows: we demonstrate that states grouped aggregated under $\epM$ have Q values all within a particular bound. Consequently $\epM$ abstractions are interpretable as an instantiation of $\epQ$ with a particular $\epsilon$ -- understanding $\epM$ abstractions allows us to conclude our bound by applying Lemma 1.

@@

\begin{align*}
B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|\\
\leq &\epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)}\left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]\\
&\text{By the similarity of transitions of grouped states under $\epM$:}\\
 \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
&\text{Applying 0-1 reward normalization and algebra:}\\
 \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
\end{align*}

Since the Q values of ground states grouped under $\epM$ are strictly less than $B$, we can understand $\epM$ as a type of $\epQ$ with $\epsilon = B$. Applying Lemma 1 yields Equation \ref{eq:lemma2}.

@@

% NChain Compression Visuals.
\begin{figure}[h]
\subfigure[Ground NChain]{
\includegraphics[width=0.48\columnwidth]{figures/ground_nchain.png}}
\subfigure[Abstract NChain]{
\includegraphics[width=0.48\columnwidth]{figures/abs_nchain.png}}
\label{fig:nchain-visual}
\caption{Comparison of Original NChain MDP and Abstract NChain MDP, under an $\epQ$ abstraction, with $\epsilon=0.5$}
\end{figure}

@@

% Taxi Compression Visuals
\begin{figure}[h]
\subfigure[Ground Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/ground_taxi.png}}
\subfigure[Abstract Taxi]{
\includegraphics[width=0.48\columnwidth]{figures/abs_taxi.png}}
\label{fig:taxi-visual}
\caption{Comparison of Original Taxi MDP and Abstract Taxi MDP, under an $\epQ$ abstraction, with $\epsilon=0.03$}
\end{figure}

@@

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Minefield MDP and Abstract MDP, under an $\epQ$ abstraction, with $\epsilon=1.1$}
\end{figure}

@@

% Random Compression Visuals
\begin{figure}
\subfigure[Ground Random]{
\includegraphics[width=0.48\columnwidth]{figures/ground_random.png}}
\subfigure[Abstract Random]{
\includegraphics[width=0.48\columnwidth]{figures/abs_random.png}}
\label{fig:minefield-visual}
\caption{Comparison of Original Random MDP and Abstract Random MDP, under an $\epQ$ abstraction, with $\epsilon=0.2$}
\end{figure}
